---
title: "NAP Progress - Aggregate"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
  
---

```{r setup, include=FALSE}
library(flexdashboard)
library(readxl)
library(magrittr)
library(plotly)
library(ggplot2)
library(dplyr)
library(reshape)
library(rpivotTable)
library(DT)
library(leaflet)

```


```{r global}
tracker<-read_excel("Open_NAPs_Database.xlsm", sheet = "tracker")
colnames(tracker)[colnames(tracker)=="Standard measure based on progress report"]<-"Measure"
tracker$Element<-factor(tracker$Element, levels = c("Laying the ground work and addressing gaps", "Preparatory elements" ,"Implementation strategies" ,"Reporting monitoring and review"))
measures<-read_excel("Open_NAPs_Database.xlsm", sheet = "Measures")
measures$`Without Measure`<-154-(measures$`Developing Countries  (non-LDC)`+measures$LDCs)
GCF_accessed<-read_excel("Open_NAPs_Database.xlsm", sheet = "GCF_Accessed")
GCF_projects<-read_excel("Open_NAPs_Database.xlsm", sheet = "GCF")
categories<-read_excel("Open_NAPs_Database.xlsm", sheet = "country_categories")
NAPS <- read_excel("Open_NAPs_Database.xlsm",sheet = "Submitted_NAPs")
country_codes_un <- read_excel("Open_NAPs_Database.xlsm",sheet = "country_codes_un")
regions <- read_excel("Open_NAPs_Database.xlsm", sheet = "UNCTAD_Regions")
iso_cat<-read_excel("Open_NAPs_Database.xlsm",sheet = "country_categories")
latlong <- read_excel("Open_NAPs_Database.xlsm",sheet = "countrylatlong")

#merge
GCF_merge<-merge(GCF_accessed, categories, by='countryname', all.x = T)
GCF_merge<-GCF_merge[,c(1,6,7,8,9,10,11)]

tracker_merge<-merge(tracker,categories, by='countryname', all.x = T)

unregions<-merge(country_codes_un, regions, by='countryname', all.x=TRUE)
unregions<-merge(unregions,iso_cat, by='countryname', all.x=TRUE)
NAPCountries<-merge(unregions,NAPS, by="countryname", all.y = TRUE)
xycountrycode<-merge(unregions,latlong, by='countryname', all.x = TRUE)
NAP_Countries<-merge(NAPS,xycountrycode, by="countryname", all.x = TRUE)
```

Progress to Formulate & Implement NAPS
==================================================================================

### Measures General Outlook

```{r}
measures$Measure<-factor(measures$Measure, levels = unique(measures$Measure)[order(measures$Code, decreasing = TRUE)])

fig <- plot_ly(measures, x = ~LDCs, y = ~Measure, type = 'bar', orientation = 'h',  name = 'LDCs',
        marker = list(color = 'rgba(38, 24, 74, 0.8)'),text=~LDCs, textposition= 'top  right',textfont=list(size=12, color='white')) 

#,line = list(color = 'rgb(248, 248, 249)', width = 1)
fig <- fig %>% add_trace(x = ~`Developing Countries  (non-LDC)`,name='Developing Countries  (non-LDC)', marker = list(color = 'rgba(71, 68, 131, 0.85)'),text=~`Developing Countries  (non-LDC)`, textposition= 'right',textfont=list(size=12, color='white')) 

fig <- fig %>% add_trace(x = ~`Without Measure`,name='Without Measure', marker = list(color = 'rgba(164, 163, 204, 0.95)'),text=~`Without Measure`, textposition= 'middle left',textfont=list(size=12, color='white')) 
fig <- fig %>% layout(xaxis = list(title = "No. of Countries",
                      showgrid = TRUE,
                      showline = FALSE,
                      showtext=T,
                      showticklabels = TRUE,
                      zeroline = FALSE,
                      domain = c(0.15, 1)),
         yaxis = list(title = "",
                      showgrid = FALSE,
                      showline = FALSE,
                      showticklabels = FALSE,
                      zeroline = FALSE),
         barmode = 'stack',
         paper_bgcolor = 'rgb(248, 248, 255)', plot_bgcolor = 'rgb(248, 248, 255)',
         margin = list(l = 200, r = 0, t = 10, b = 50),
         showlegend = TRUE, legend=list(orientation='h', x=0.2,y=-0.15))

# label yaxis
fig <- fig %>% add_annotations(xref = 'paper', yref = 'y', x = 0.14, y = ~Measure,
                  xanchor = 'right',
                  text = paste(measures$Code, '-',measures$Measure1),
                  font = list(family = 'Arial', size = 12,
                            color = 'rgb(67, 67, 67)'),
                  showarrow = FALSE, align = 'center') 


 
#add_annotations(text = paste0(df$percentage, "%"), x = df$QuarterYear, 
                 # y = unlist(tapply(df$percentage, df$QuarterYear, FUN=cumsum))-(df$percentage/2), 
                  #showarrow = FALSE)


 

fig

```



Select Measures
=========================================================================================
{.tabset }
---------------------------------------------
### General Outlook
```{r}
mselect<-measures%>%dplyr::filter(Code=='A1'|Code=='A2'|Code=='A3'|Code=='A8'|Code=='A9'|Code=='B3'|Code=='B7'|Code=='C3'|Code=='D4')

mselect$Measure<-factor(mselect$Measure, levels = unique(mselect$Measure)[order(mselect$Code, decreasing = TRUE)])

fig <- plot_ly(mselect, x = ~LDCs, y = ~Measure, type = 'bar', orientation = 'h', text=~LDCs, textposition= 'left',textfont=list(size=12, color='white'), name = 'LDCs',
        marker = list(color = 'rgba(38, 24, 74, 0.8)')) 

#,line = list(color = 'rgb(248, 248, 249)', width = 1)
fig <- fig %>% add_trace(x = ~`Developing Countries  (non-LDC)`,name='Developing Countries (non-LDC)', marker = list(color = 'rgba(71, 68, 131, 0.85)'),text=~`Developing Countries  (non-LDC)`, textposition= 'right',textfont=list(size=12, color='white')) 

fig <- fig %>% add_trace(x = ~`Without Measure`,name='Without Measure', marker = list(color = 'rgba(164, 163, 204, 0.95)'),text=~`Without Measure`, textposition= 'middle',textfont=list(size=12, color='white')) 
fig <- fig %>% layout(xaxis = list(title = "No. of Countries",
                      showgrid = TRUE,
                      showline = FALSE,
                      showtext=T,
                      showticklabels = TRUE,
                      zeroline = FALSE,
                      domain = c(0.15, 1)),
         yaxis = list(title = "",
                      showgrid = FALSE,
                      showline = FALSE,
                      showticklabels = FALSE,
                      zeroline = FALSE),
         barmode = 'stack',
         paper_bgcolor = 'rgb(248, 248, 255)', plot_bgcolor = 'rgb(248, 248, 255)',
         margin = list(l = 200, r = 0, t = 10, b = 50),
         showlegend = TRUE, legend=list(orientation='h', x=0.2,y=-0.15))

# label yaxis
fig <- fig %>% add_annotations(xref = 'paper', yref = 'y', x = 0.14, y = ~Measure,
                  xanchor = 'right',
                  text = paste(mselect$Code, '-',mselect$Measure),
                  font = list(family = 'Arial', size = 12,
                            color = 'rgb(67, 67, 67)'),
                  showarrow = FALSE, align = 'center') 



 
fig

```

#### Important Measures -  general

```{r}
#selected_measures<-measures%>%dplyr::filter(Code=='A1'|Code=='A2'|Code=='A3'|Code=='A8'|Code=='A9'|Code=='B3'|Code=='B7'|Code=='C3'|Code=='D4')
selected_measures<-tracker_merge%>%dplyr::filter(`Measure code`=='A1'|`Measure code`=='A2'|`Measure code`=='A3'|`Measure code`=='A8'|`Measure code`=='A9'|`Measure code`=='B3'|`Measure code`=='B7'|`Measure code`=='C3'|`Measure code`=='D4')

df<-selected_measures%>%group_by(Element,Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
plot_ly(df,type='bar',x=paste(df$`Measure code`, substr(df$Measure, 1,40), '...', sep = '-'),y=~Countries, text=~Countries, textposition='auto', color = ~Measure, colors = 'Reds',legendgroup=~Measure, showlegend=F)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "Measure"),yaxis=list(title='No. of Countries'))

```


### By Region

```{r}

africa<-selected_measures%>%filter(Region=='Africa')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
af_plot<-plot_ly(africa,type='bar',x=paste(africa$`Measure code`, substr(africa$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds',legendgroup=~Measure, showlegend=F)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "Africa"),yaxis=list(title='No. of Countries'))


asia_pacific<-selected_measures%>%filter(Region=='Asia-Pacific')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
asia_plot<-plot_ly(asia_pacific, type='bar',x=paste(asia_pacific$`Measure code`, substr(asia_pacific$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds',legendgroup=~Measure, showlegend=F)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "Asia-Pacific"),yaxis=list(title='No. of Countries'))


lac<-selected_measures%>%filter(Region=='LAC')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
lac_plot<-plot_ly(lac,type='bar',x=paste(lac$`Measure code`, substr(lac$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds',legendgroup=~Measure, showlegend=F)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "LAC"),yaxis=list(title='No. of Countries'))


eu<-selected_measures%>%filter(Region=='Eastern Europe')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
eu_plot<-plot_ly(eu,type='bar',x=paste(eu$`Measure code`, substr(eu$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds',legendgroup=~Measure, showlegend=F)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "Eastern Europe"),yaxis=list(title='No. of Countries'))


plotly::subplot(af_plot, asia_plot,lac_plot,eu_plot, titleX = T,shareY = T, margin = 0.02)%>% layout(barmode = 'stack',plot_bgcolor='#e5ecf6')

```

#### Important Measures by Country Category

```{r}

ldc<-selected_measures%>%filter(Category=='LDC')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
ldc_plot<-plot_ly(ldc,type='bar',x=paste(ldc$`Measure code`, substr(ldc$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds', showlegend=F)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "LDC"),yaxis=list(title='No. of Countries'))


sids<-selected_measures%>%filter(Category=='SIDS')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
sids_plot<-plot_ly(sids, type='bar',x=paste(sids$`Measure code`, substr(sids$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds', showlegend=F)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "SIDS"),yaxis=list(title='No. of Countries'))


ldc_sids<-selected_measures%>%filter(Category=='LDC, SIDS')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
ldc_sids_plot<-plot_ly(ldc_sids, type='bar',x=paste(ldc_sids$`Measure code`, substr(ldc_sids$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds', showlegend=T)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "LDC,SIDS"),yaxis=list(title='No. of Countries'))


lldc<-selected_measures%>%filter(Category=='LLDC')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
lldc_plot<-plot_ly(lldc, type='bar',x=paste(lldc$`Measure code`, substr(lldc$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds', showlegend=F)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "LLDC"),yaxis=list(title='No. of Countries'))


ldc_lldc<-selected_measures%>%filter(Category=='LDC, LLDC')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
ldc_lldc_plot<-plot_ly(ldc_lldc, type='bar',x=paste(ldc_lldc$`Measure code`, substr(ldc_lldc$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds', showlegend=F)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "LDC,LLDC"),yaxis=list(title='No. of Countries'))


otherdc<-selected_measures%>%filter(Category=='Other developing country')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
otherdc_plot<-plot_ly(otherdc,type='bar',x=paste(otherdc$`Measure code`, substr(otherdc$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds',legendgroup=~Measure, showlegend=F)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "Other DC"),yaxis=list(title='No. of Countries'))


plotly::subplot(ldc_plot,sids_plot,ldc_sids_plot,lldc_plot,ldc_lldc_plot,otherdc_plot, titleX = T,shareY = T)%>% layout(barmode = 'stack', showlegend = F)


```

### By Country Category

```{r}

ldc<-selected_measures%>%filter(Category2=='LDC')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
ldc_plot<-plot_ly(ldc,type='bar',x=paste(ldc$`Measure code`, substr(ldc$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds', showlegend=F)%>%
  plotly::layout(name = "LDC",barmode='stack', xaxis = list(title = " LDC"),yaxis=list(title='No. of Countries'))


otherdc<-selected_measures%>%filter(Category2=='Other developing country')%>% group_by(Measure,`Measure code`)%>%count(Country)%>%
  summarise('Countries'=sum(n))
otherdc_plot<-plot_ly(otherdc,type='bar',x=paste(otherdc$`Measure code`, substr(otherdc$Measure, 1,40), '...',sep = '-'),y=~Countries, color = ~Measure, colors = 'Reds',legendgroup=~Measure, showlegend=F, name='Other DC')%>%
  plotly::layout(barmode='stack', xaxis = list(title = "Other DC"),yaxis=list(title='No. of Countries'))



plotly::subplot(ldc_plot,otherdc_plot, titleX = T,shareY = F, margin = 0.05)%>% layout(barmode = 'stack', plot_bgcolor='#e5ecf6', showlegend = F)


```

###### Measures Select- Outlook

```{r}
mshort<-selected_measures[,c(3,5,6,7,8,19)]%>%group_by(Measure, Category2, `Measure code`)%>%count(Country)%>%summarise("Countries"=sum(n))
mshort$`Measure code`<-factor(mshort$`Measure code`, levels = unique(mshort$`Measure code`)[order(mshort$`Measure code`, decreasing = TRUE)])
#mshort%>%group_by(Measure)%>%count(Country)%>%summarise("Countries"=sum(n))
plot_ly(mshort, type='bar', x=~Countries, y=paste(mshort$`Measure code`,':', substr(mshort$Measure, 1, 40), '...'), fill=~Category2, color = ~Category2)%>%plotly::layout(barmode='stack')

#ggplot(mshort)+
 # geom_bar(stat = 'identity', aes(x=Countries, y=paste(mshort$`Measure code`, ':', substr(mshort$Measure, 1, 40), '...'), fill=Category2, #colour=Category2))
```


Find full of measures[here](do we have a sharable link for the measures?)

NAP Submissions
========================================================

### Countries with submitted NAPS

```{r}

NAP_Countries$`Document title`<-paste('<a href=',NAP_Countries$Link, '>',NAP_Countries$`Document title`,'</a>', sep = "")

NAP_Countries<-NAP_Countries%>%
   mutate(popup_info=paste(countryname,"<br>","Submitted on:",NAP_Countries$`Date of submission`,"<br>","Title:",NAP_Countries$`Document title`))

leaflet(NAP_Countries)%>%setView(lng= 35.79, lat= -10 , zoom = 2.42)%>%
  addTiles()%>%
  addCircleMarkers(data=NAP_Countries, fill=T,lng=~lon, lat =~lat, radius = 6, color='red', popup =~popup_info)
 
```

##### List
```{r}
NAPS$`Document title`<-paste('<a href=',NAPS$Link, '>',NAPS$`Document title`,'</a>', sep = "")

colnames(NAPS)[colnames(NAPS)=='countryname']<-'Country'
#colnames(GCF_projects)[colnames(GCF_projects)=='Region_init']<-'Region'
naps<-NAPS[,-4]
datatable(naps,filter = 'top',selection = 'multiple',callback = JS("return table;"), fillContainer = T,rownames = F, editable = F, style = 'jqueryui', class = 'display responsive', width = '100%', caption = "GCF Projects", extensions = 'Buttons', options=list(initComplete = JS("function(settings, json) {$(this.api().table().header()).css({'font-size' : '70%'});}"),pageLength= 10, dom='lfrtipB', buttons = c('copy', 'csv', 'excel', 'pdf')), escape = F)%>%
  DT::formatStyle(columns = colnames(naps),fontSize= '12px')
 
```



GCF Resources
===============================================================
{.tabset}
---------------------------------------------------------------

### Total Funding - by Country

```{r}
country_tot<-GCF_merge%>%dplyr::filter(`Grand Total`>0.0)%>%group_by(countryname)%>%summarise('Total'=sum(`Grand Total`))

country_tot$countryname <- factor(country_tot$countryname, levels = unique(country_tot$countryname)[order(country_tot$Total, decreasing =FALSE)])

p<-ggplot(country_tot)+
  geom_bar(stat='identity', aes(x=countryname,y=Total), colour='white',fill='blue')+
  labs(x='Country', y='Amount Accessed (Million USD)')+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1, size = 13), axis.text.y = element_text(size = 13), axis.title.y = element_text(size = 13), axis.title.x = element_blank())
ggplotly(p)

```


### Total Funding - LDC
```{r}
ldc<-GCF_merge%>%filter(Category2=='LDC')%>% filter(`Grand Total`>0.0)%>% group_by(countryname, Category2)%>%summarise('Total'=sum(`Grand Total`))
ldc$countryname <- factor(ldc$countryname, levels = unique(ldc$countryname)[order(ldc$Total, decreasing = TRUE)])

plot_ly(ldc,type='bar',x=~countryname,y=~Total, color = ~Category2, colors = 'Blue', showlegend=F)%>%
  plotly::layout(barmode='stack', xaxis = list(title = "", tickangle=90, tickfont=list(size=22)),yaxis=list(range=c(0,450), tickfont=list(size=20), title='Total Amount ((Million USD)', titlefont=list(size=20)))
```

### Total Funding - Other DC
```{r}
otherdc<-GCF_merge%>%filter(Category2=='Other developing country')%>% filter(`Grand Total`>0.0)%>% group_by(countryname, Category2)%>%summarise('Total'=sum(`Grand Total`))
otherdc$countryname <- factor(otherdc$countryname, levels = unique(otherdc$countryname)[order(otherdc$Total, decreasing = TRUE)])

plot_ly(otherdc,type='bar',x=~countryname,y=~Total, color = ~Category2, colors = 'Blue', showlegend=F)%>%
 plotly::layout(barmode='stack', xaxis = list(title = "", tickangle=90, tickfont=list(size=15.85)),yaxis=list(range=c(0,450), tickfont=list(size=18), title='Total Amount ((Million USD)', titlefont=list(size=18)))
```
```{r}

ldc1<-ldc
ldc1$Total<-as.integer(ldc1$Total)
write.table(ldc1, file = 'ldc1.txt', sep = "", row.names = F)

otherdc1<-otherdc
otherdc1$Total<-as.character(otherdc1$Total)
write.table(otherdc1, file = 'otherdc1.csv', sep = "", row.names = F)

```


GCF - Other
=====================================================
{data-orientation=columns}
-----------------------------------------------------

### Readiness

```{r}

country_red<-GCF_merge%>%dplyr::filter(`Grand Total`>0.0)%>%group_by(countryname)%>%summarise('Total'=sum(`Readiness support approved`))

country_red$countryname <- factor(country_red$countryname, levels = unique(country_red$countryname)[order(country_red$Total, decreasing = F)])

  plot_ly(data=country_red, type='bar', 
          y=~countryname,
          x=~Total)%>%
    plotly::layout(title='Readiness Amount Approved - by Country',yaxis=list(title=''), xaxis=list(title='Readiness Amount Approved (Million USD)'))
```

### Project Funding

```{r}

country_proj<-GCF_merge%>%dplyr::filter(`Total GCF financing (projects)`>0.0)%>%group_by(countryname)%>%summarise('Total'=sum(
  `Total GCF financing (projects)`
))

country_proj$countryname <- factor(country_proj$countryname, levels = unique(country_proj$countryname)[order(country_proj$Total, decreasing = F)])

  plot_ly(data=country_proj, type='bar', 
          y=~countryname,
          x=~Total)%>%
    plotly::layout(title='Total Project Financing - by Country',yaxis=list(title=''), xaxis=list(title='Project Amount (\'000 USD)'))
```

Projects
======================================================
### Projects
__To do:__ check if we have links to project websites or project files somewhere

```{r}
library(DT)
#GCF_projects$`Project Name`<-paste('<a href=',GCF_projects$Link, '>',GCF_projects$`Project Name`,'</a>', sep = "")

colnames(GCF_projects)[colnames(GCF_projects)=='countryname']<-'Country'
colnames(GCF_projects)[colnames(GCF_projects)=='Region_init']<-'Region'

proj<-GCF_projects[,c(2,3,5,8,10)]
datatable(proj,filter = 'top',selection = 'multiple',callback = JS("return table;"), fillContainer = T,rownames = F, editable = F, style = 'jqueryui', class = 'display responsive', width = '100%', caption = "GCF Projects", extensions = 'Buttons', options=list(initComplete = JS("function(settings, json) {$(this.api().table().header()).css({'font-size' : '70%'});}"),pageLength= 5, dom='lfrtipB', buttons = c('copy', 'csv', 'excel', 'pdf')), escape = F)%>%
  DT::formatStyle(columns = colnames(proj),fontSize= '12px')


```


Explore with pivot table
=================================================
__Hint__
Select desired graphic to draw from the drop-down menu on the first column   
Drag-&-Drop the variable(s) of interest from the first column into the second column,    
Then from the drop down menu on the second column select how you want to represent your values e.g as a Count, Sum, List, etc   

```{r}
rpivotTable(data=tracker, cols =~Country,   rendererName ='Horizontal Stacked Bar Chart' )
#rows = ~Measure,vals = 'Measure', aggregatorName = 'Count Unique Values',
```




